Simulation-WTCCC-2

### 2020-03-13 analysis/simulation-WTCCC2.Rmd
v1.0 simulate expression using separate data 20191127

---
title: "Simulation-WTCCC"
output: html_document
---

@@

@@

## Simulate quantitative phenotype

@@

```{r}
simudir <- "/home/simingz/causalTWAS/simulations/simulation_WTCCC_20191111/"
show_res <- function(simutag){
  load(Sys.glob(paste0(simudir,simutag,"*phenotype.Rd")))
  outdf1 <- data.frame(truth = c(sigma_gamma^2*J.c, sigma_theta^2*M.c , 1))
  row.names(outdf1) <- c("sigma_gamma^2","sigma_theta^2","sigma_e^2")
  res <- readLines(paste0(simudir, simutag, "_VC/output/", simutag, ".log.txt"))
  outdf1$est <- as.numeric(strsplit(res[24], "  ")[[1]][2:4])
  outdf1$est.se <- as.numeric(strsplit(res[25], "  ")[[1]][2:4])
  print(outdf1)
  outdf2 <- data.frame("est"= c(as.numeric(strsplit(res[20], "  ")[[1]][2:3]), as.numeric(strsplit(res[22], "=")[[1]][2])))
  row.names(outdf2) <- c("PVE.expr","PVE.snp","PVE.total")
  outdf2$est.se <- c(as.numeric(strsplit(res[21], "  ")[[1]][2:3]), as.numeric(strsplit(res[23], "=")[[1]][2]))
  print(outdf2)
}
```

@@

## Simulation 4: $M$ = ~ 1% all SNPs (M=5000), $J$ = ~10% all genes (J=2000)

### 4.1 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.1$ 
```{r 4.1}
show_res("S4.1")
```

### 4.2 $PVE_{SNP} \approx 0.4$, $PVE_{expr} \approx 0.1$
```{r 4.2}
show_res("S4.2")
```

>>>>

---
title: "Simulation-WTCCC-2"
output: html_document
---

@@

The difference between this analysis and [previous run](simulation-WTCCC.html): used 500 samples from `cad.RData` from WTCCC to simulate expression, then train expression model using `cv.glmnet`. We impute expression in using `bd.RData` from WTCCC.

Simulation of phenotype: use the same weights as used in simulate expression using the `'cad.RData` dataset.

The genotype data and other settings are the same.

@@

## Simulate quantitative phenotype
We simulate phenotype followin

@@

```{r}
simudir <- "/home/simingz/causalTWAS/simulations/simulation_WTCCC_20191127/"
show_res <- function(simutag){
  load(Sys.glob(paste0(simudir,simutag,"*phenotype.Rd")))
  outdf1 <- data.frame(truth = c(sigma_gamma^2*J.c, sigma_theta^2*M.c , 1))
  row.names(outdf1) <- c("sigma_gamma^2","sigma_theta^2","sigma_e^2")
  res <- readLines(paste0(simudir, simutag, "_VC/output/", simutag, ".log.txt"))
  outdf1$est <- as.numeric(strsplit(res[24], "  ")[[1]][2:4])
  outdf1$est.se <- as.numeric(strsplit(res[25], "  ")[[1]][2:4])
  print(outdf1)
  outdf2 <- data.frame("est"= c(as.numeric(strsplit(res[20], "  ")[[1]][2:3]), as.numeric(strsplit(res[22], "=")[[1]][2])))
  row.names(outdf2) <- c("PVE.expr","PVE.snp","PVE.total")
  outdf2$est.se <- c(as.numeric(strsplit(res[21], "  ")[[1]][2:3]), as.numeric(strsplit(res[23], "=")[[1]][2]))
  print(outdf2)
}
```

@@
